TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-04 paper/paper.tex
Updated methods

	\subsection{Comparing Performance}
	One scenario will be used to compare the performance of the TCP congestion algorithms:
	\begin{enumerate}
		\item The user owns multiple endpoints in the network. In this case a congestion algorithm is applied at both the client and server side. This scenario applies to multitentant datacenter situations, where a user owns a server in the datacenter network and a node outside of the datacenter network.
	\end{enumerate}

@@

	In both scenarios the TCP congestion algorithms are tested for multiple characteristics:
	\begin{enumerate}
		\item TCP Window Size measured over time: to determine whether using a specific TCP congestion algorithm in combination with other TCP congestion algorithms results in the allocation of a larger window or a smaller window to a specific TCP connection.
		\item Bandwidth allocation: to determine whether using a specific TCP congestion algorithm in combination with other TCP congestion algorithms results in the allocation of more bandwidth to a specific TCP connection.
		\item Round Trip Time: to determine the reason of the behaviour of a TCP congestion algorithm in combination with other TCP congestion algorithms.
	\end{enumerate}
The tests conducted on the algorithms have two environment variables: packet loss and delay. Those environment variables are simulated using \texttt{netem}, which is a network emulation functionality in several Linux distributions \cite{linux-netem}. Packet loss and delay are chosen as the behavior of most TCP algorithms depend on those variables [SRC]. The values for the environment variables are chosen based on measurements performed by Verizon \cite{verizon-latency}.

@@

		\subsubsection{Performing time-based automated tests}
		The tests will be performed using scripts written in Python [\ref{appendix:python}]. The scripts either act as controller or as disciple. The controller is responsible for controlling the tests, by synchronizing the time, exchanging commands to run, modify or stop the tests and gathering data. The disciple is the listener and executes all task commands the controller sends. The commands include getting the hostname of a disciple, setting the TCP congestion algorithm of a disciple, configuring the time of a disciple, starting the data transfer from a disciple and closing the connection with the controller.

@@

		\subsubsection{Algorithm Characteristics}
		- Includes characteristics of the algorithms. To what do the TCP congestion algorithms respond according to literature? And how do they deal with that (If available in literature).

>>>>

	\subsection{Comparing Performance}
	One scenario will be used to compare the performance of the TCP congestion algorithms:
	\begin{enumerate}
		\item The user owns multiple endpoints in the network. In this case a congestion algorithm is applied at both the client and server side. This scenario applies to multitentant datacenter situations, where a user owns a server in the datacenter network and a node outside of the datacenter network. In this test the user node and random node(s) are at the receiving side and the user server and random server at the sending side. The tests will be performed from a multitenant datacenter perspective.
	\end{enumerate}

@@

	In scenario 1 the TCP congestion algorithm is tested for fairness in sharing bandwidth with other TCP connections using other TCP congestion algorithms. In order to test the fairness of bandwidth shares, the bandwidth allocation per algorithm is measured. It can be determined whether a specific TCP congestion algorithm in combination with other TCP congestion algorithms results in the allocation of more or less bandwidth to that specific TCP connection.

The tests conducted on the algorithms have two environment variables: packet loss and delay. Those environment variables are simulated using \texttt{netem}, which is a network emulation functionality in several Linux distributions \cite{linux-netem}. \texttt{netem} is applied to the incoming side of the interfaces of the clients to emulate the same packet loss and delay. Windows, which is tested as a server, does not support \texttt{netem}. Therefore the packet loss and delay are applied to the incoming interfaces of the clients. Packet loss and delay are chosen as the behavior of most TCP algorithms depends on those variables [SRC]. The values for the environment variables are chosen based on measurements performed by Verizon \cite{verizon-latency}.

%\item TCP Window Size measured over time: to determine whether using a specific TCP congestion algorithm in combination with other TCP congestion algorithms results in the allocation of a larger window or a smaller window to a specific TCP connection.
% \item Round Trip Time: to determine the reason of the behaviour of a TCP congestion algorithm in combination with other TCP congestion algorithms.

@@

		\subsubsection{Performing time-based automated tests}
		The tests will be performed using scripts written in Python [\ref{appendix:python}]. The scripts either act as controller or as disciple. The controller is responsible for controlling the tests, by synchronizing the time, exchanging commands to run, modify or stop the tests and gathering data. The disciple is the listener and executes all task commands the controller sends. The commands include getting the hostname of a disciple, setting the TCP congestion algorithm of a disciple, configuring the time of a disciple, starting the data transfer and measurement tools on the disciple and closing the connection with the controller.

@@

		\subsubsection{Algorithm Characteristics}

		- Includes characteristics of the algorithms. To what do the TCP congestion algorithms respond according to literature? And how do they deal with that (If available in literature).
